DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox

### 2017-06-05 ase2017/paper.tex
minor change
reviewed illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den'' 
represent the numerator $A(z)$ and denominator $B(z)$, respectively.
%
\begin{equation}
\label{equation_plant}
G(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}
%
\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983 z^2 + 0.09587 z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665 z + 0.75
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}
%
In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
the synthesized stable digital controller, which could be expressed in Eq.(\ref{equation_controller}).

@@

In addition, a digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; poles must have the modulus less than one. In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} to achieve a general equation regarding the transfer-function representation. The general equation that represents the combination between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

Applying the FWL effects in the $D(z)$ in order to compute the roots for stability reproduction, then if any root has modulus equal or greater than one, then the system is unstable; otherwise, it is stable. In fact, the roots computed by the function \texttt{roots} in MATLAB~\cite{matlab-toolbox} resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.

>>>>

To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
which represents a UAV a quadcopter system, described by 
Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) 
is represented using the transfer-function format, where ``num'' and ``den'' 
represent the numerator $A(z)$ and denominator $B(z)$, respectively.
%
\begin{equation}
\label{equation_plant}
G(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
\end{equation}
%
\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983 z^2 + 0.09587 z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665 z + 0.75
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}
%
In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
the synthesized stable digital controller, which can be expressed in Eq.(\ref{equation_controller}).

@@

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; 
poles must have the modulus less than one. In order to compute the poles from the digital 
system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) 
and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} 
commands in MATLAB~\cite{matlab-toolbox} to achieve a general equation regarding the 
transfer-function representation. The general equation that represents the combination 
between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

After applying FWL effects in $D(z)$ to compute the roots for stability reproduction, 
if any root has modulus equal or greater than one, then the system is unstable; 
otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
in MATLAB~\cite{matlab-toolbox} result in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, 
which means that DSSynth has synthesized a stable digital controller.
